CRUSE to Safe Cycling in Ireland \\\large{An Open Source Tool to Support Active Travel}

### 2023-10-11 paper.qmd
Only build html

# # Uncomment for draft versions:
format: 
  html: default
  # docx: default
# # Uncomment for formatted version
#   elsevier-pdf:
#     linestretch: 2
#     keep-tex: true
#     journal:
#       name: European Transport Research Review
#       formatting: preprint
#       model: 3p
#       cite-style: super
# # #   # pdf: default

>>>>

# # Uncomment for draft versions:
format: 
  html: default
  # docx: default
# # # Uncomment for formatted version
#   elsevier-pdf:
#     linestretch: 2
#     keep-tex: true
#     journal:
#       name: European Transport Research Review
#       formatting: preprint
#       model: 3p
#       cite-style: super
# # #   # pdf: default

### 2023-10-11 paper.tex
Only build html

This paper describes the design, features and potential use of the Cycle
Route Acceptance and Scenario Estimation (CRUSE) Tool for Ireland was
commissioned to support cycle network planning, safety interventions,
business cases and project evaluation. The resulting web application is
available at \url{https://cruse.bike/}, enabling planners, engineers,
and other stakeholders to make more evidence-based decisions. CRUSE goes
beyond previous work in several important ways. It models networks at
high levels of geographic resolution, simulates a wide range of trips
including recreational, social, shopping and personal trips, in addition
to trips to work and primary, secondary and tertiary education
locations. The tool provides key `denominator' information to enable
reporting of collision rates per billion km cycled.

@@

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

>>>>

This paper describes the design, features and potential use of the Cycle
Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland was
commissioned to support cycle network planning, safety interventions,
business cases and project evaluation. The resulting web application is
available at \url{https://cruse.bike/}, enabling planners, engineers,
and other stakeholders to make more evidence-based decisions. CRUSE goes
beyond previous work in several important ways. It models networks at
high levels of geographic resolution, simulates a wide range of trips
including recreational, social, shopping and personal trips, in addition
to trips to work and primary, secondary and tertiary education
locations. The tool provides key `denominator' information to enable
reporting of collision rates per billion km cycled.

@@

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi
